### 2019-11-14 fragments/gale-elsen-hooker.tex
typo fixes and references

Deep networks achieve state-of-the-art performance on many practical tasks, including
image recognition \citep{citation_needed}, speech synthesis \citep{citation_needed},
automatic translation \citep{citation_needed}. Although performance tends to improve
with the model size, training and deploying large models becomes challenging. Several
aprroaches tackling this are being acitvely developed: model compression \citep{pruning},
distillation \citep{distill} and sparsification. The latter one essentially reduces
the numerical and storage complexity by zeroing as many parameters of the model as
possbile without significant performance loss. This has foremost importance in resource
constrained applications, such as embedded systems and mobile devices.

sparisity inducing methods impose structure on the topology of sparse weights
unstructured -- gives the achievable maximum of the compression-accuracy tradeoff, but
poses challenges in practical implementations (popr chace performance, almost as if
random access model).

Learnt Sparse topology can be trained from scratch to full performance (this is what
we use in train-compressed phase). reinitialization or continuation. But Gale et al.
faield to replicate successfull training from scratch (even for longer training), and
the results were worse than mag-prune. the likely reason is the complexity of the task
and scale of the models.

Sparsification techniques demonstrated deliver sota compression on small models / datasets,
perform inconsistently, and that simple heiristic approaches yield better results with less
computational costs. And provide strong counterexamples to reusability of the learnt sparse
topology.

% their paper
goal: apply sparsity inducing techniques to large-scale models and datasets
\citet{galehooker} raise an important issue that all sparsification techniques have been
propsed and tested on relatively small models, and skew towards convolutional architectures.
Sparsification is like architecture search: the space being the connectivity the computational
graph of the model. Evaluate smooth $\ell_0$ regularization \citep{louizos}, variational
dropout \citep{kingma2015} and magnitude pruning \citep{zhu-gupta2017} \ref{datasets}.

@@

(resnet) ResNet-50 (He et al. 2016) on ImageNet. 128k iter x 1024 batch 
SGD w. mom; lr ramp-up 5ep. up 0.4, ÷ 10 every 30ep, see TF resnet-50
Sparsify conv and fc layers. Vardropout experimetns used batches of size 32 over 32 accel.

(xformer) Neural Machine Translation Transformer (Vasawi et al.2017) on WMT 2014 Eng-Ger dual corpus
standard procedire from (Vasawi et al.2017) without checkpoint averaging. Sparsify fc (attn) and
embedding layers.

@@

(resnet) unenven distribution of sparsity through the network

@@

these are the techniques for cplx-sparsification. THey alllow this tradeoff on such and
such models.

>>>>

Deep networks achieve state-of-the-art performance on many practical tasks, including
image recognition \citep{citation_needed}, speech synthesis \citep{citation_needed},
automatic translation \citep{citation_needed}. Although performance tends to improve
with the model size, training and deploying large models becomes challenging. Several
aprroaches tackling this are being actively developed: model compression \citep{pruning},
distillation \citep{distill} and sparsification. The latter one essentially reduces
the numerical and storage complexity by zeroing as many parameters of the model as
possbile without significant performance loss. This has foremost importance in resource
constrained applications, such as embedded systems and mobile devices.

sparisity inducing methods impose structure on the topology of sparse weights
unstructured -- gives the achievable maximum of the compression-accuracy tradeoff, but
poses challenges in practical implementations (poor cache performance, almost as if
random access model).

Learnt Sparse topology can be trained from scratch to full performance (this is what
we use in train-compressed phase). reinitialization or continuation. But Gale et al.
failed to replicate successful training from scratch (even for longer training), and
the results were worse than mag-prune. the likely reason is the complexity of the task
and scale of the models.

Sparsification techniques demonstrated deliver sota compression on small models / datasets,
perform inconsistently, and that simple heuristic approaches yield better results with less
computational costs. And provide strong counterexamples to reusability of the learnt sparse
topology.

% their paper
goal: apply sparsity inducing techniques to large-scale models and datasets
\citet{galehooker} raise an important issue that all sparsification techniques have been
proposed and tested on relatively small models, and skew towards convolutional architectures.
Sparsification is like architecture search: the space being the connectivity the computational
graph of the model. Evaluate smooth $\ell_0$ regularization \citep{louizos}, variational
dropout \citep{kingma2015} and magnitude pruning \citep{zhu-gupta2017} \ref{datasets}.

@@

(resnet) ResNet-50 (He et al. 2016) on ImageNet. 128k iter x 1024 batch 
SGD w. mom; lr ramp-up 5ep. up 0.4, ÷ 10 every 30ep, see TF resnet-50
Sparsify conv and fc layers. Vardropout experiments used batches of size 32 over 32 accel.

(xformer) Neural Machine Translation Transformer (Vasawi et al.2017) on WMT 2014 Eng-Ger dual corpus
standard procedure from (Vasawi et al.2017) without checkpoint averaging. Sparsify fc (attn) and
embedding layers.

@@

(resnet) uneven distribution of sparsity through the network

@@

these are the techniques for cplx-sparsification. THey allow this trade-off on such and
such models.

### 2019-11-14 fragments/monning-manandhar.tex
typo fixes and references

the paper studies capacity of simple complex networks
conclude that cplx nets perform not better than real-valued netowrks with similar capacity.
Observe synchronisation of real and imaginary parts in real valued tasks, but observe subpar
performance of cplx netowrks of equal capacity, sensetivity ot initialization. Isues due to 
singularities (poles) -- avoidable by constraining function value, normalizing weights or
gradients. Found that using relus is stabler and allows insight transfer from the vast literature
on real nets to complex domain. Recommend using cplx only if the data naturally or meaningfully
maps into cplx plane. and the net should reflect real-imag interaction

ensure comparability of architectures with respect to model size and capacity: doubling of
the number of parameters implies that one should keep the number of numerical parameters as
close as possible whn comparing real and complex nets. This ensures that performance differences
are due to use of cplx numbers rather than doubling of the number of parameters.
1) fixed number of real-valued parameters per layer
2) fixed budget of real-valued parameters per network

(lit-review) formally described in [8], complex versions of backpropagation in [6, 10, 19],
ides were even extended to quaternions [4, 3], complex valued RNN [5, 29] with unitary matrices
to tackle vanishing/exploding gradient problems. Complex convolutions [26], and complex attention
layers for complex-valeud transformer achitectures [ynag-ma-li]
Complex version of  batch-normalisation and weight initialization [26] (analogue of glorot xavier)

cplx-nets had limited popularity: less intuitive architecutres, increased numerical complexity (in
paired real -- instead of a single up to four multiplications are required, and two additions).
% due to them not being true cplx and just paired real computational graphs

(tasks) processing and analysis of compelx-valued data or data with intuitive mapping to
complex numbers. Images and signals in spectral representation. [15] show superiority of complex
nets to such tasks.

@@

(cplx) activation function can be C->C or C->R. cplx-differentiable -- exists limit in
C-field -- holomorhpic. Wirtinger CR calculus -- chosing a different basis of partial derivatives
CR improves statbility of the training process.

@@

[03] Aizenberg (2007) Multilayer feedfroward network on multi-valued neurons and back prop
[04] Aizenberg (1992) Cnn based on muli-valeud neurons 
[05] Arjovsky, Shah (2015) Unitary evolution recurrent neural networks
[06] Benvenuto, Piazza (1992) complex backprop algorithm
[08] Clarke (1990) Generalization on neural networks to compelx plane
[10] Gergious Koutsougeras (1992) Complex domain backpropagation
[15] Hirose (2009) Cmoplex valued neural networks
[19] Nitta (1993) A back-propagation algorithm for compelx numbered neural networks
[26] Trabelsi (2017) Deep complex networks
[29] Wisdom Powers (2016) Full-capacity unitary recurrent neural networks

>>>>

the paper studies capacity of simple complex networks
conclude that cplx nets perform not better than real-valued networks with similar capacity.
Observe synchronisation of real and imaginary parts in real valued tasks, but observe subpar
performance of cplx networks of equal capacity, sensitivity ot initialization. Isues due to 
singularities (poles) -- avoidable by constraining function value, normalizing weights or
gradients. Found that using ReLUs is stabler and allows insight transfer from the vast literature
on real nets to complex domain. Recommend using cplx only if the data naturally or meaningfully
maps into cplx plane. and the net should reflect real-imag interaction

ensure comparability of architectures with respect to model size and capacity: doubling of
the number of parameters implies that one should keep the number of numerical parameters as
close as possible when comparing real and complex nets. This ensures that performance differences
are due to use of cplx numbers rather than doubling of the number of parameters.
1) fixed number of real-valued parameters per layer
2) fixed budget of real-valued parameters per network

(lit-review) formally described in [8], complex versions of backpropagation in [6, 10, 19],
ides were even extended to quaternions [4, 3], complex valued RNN [5, 29] with unitary matrices
to tackle vanishing/exploding gradient problems. Complex convolutions [26], and complex attention
layers for complex-valued transformer architectures [ynag-ma-li]
Complex version of  batch-normalisation and weight initialization [26] (analogue of glorot xavier)

cplx-nets had limited popularity: less intuitive architectures, increased numerical complexity (in
paired real -- instead of a single up to four multiplications are required, and two additions).
% due to them not being true cplx and just paired real computational graphs

(tasks) processing and analysis of complex-valued data or data with intuitive mapping to
complex numbers. Images and signals in spectral representation. [15] show superiority of complex
nets to such tasks.

@@

(cplx) activation function can be C->C or C->R. cplx-differentiable -- exists limit in
C-field -- holomorhpic. Wirtinger CR calculus -- choosing a different basis of partial derivatives
CR improves stability of the training process.

@@

[03] Aizenberg (2007) Multilayer feedfroward network on multi-valued neurons and back prop
[04] Aizenberg (1992) Cnn based on muli-valued neurons 
[05] Arjovsky, Shah (2015) Unitary evolution recurrent neural networks
[06] Benvenuto, Piazza (1992) complex backprop algorithm
[08] Clarke (1990) Generalization on neural networks to complex plane
[10] Gergious Koutsougeras (1992) Complex domain backpropagation
[15] Hirose (2009) Complex valued neural networks
[19] Nitta (1993) A back-propagation algorithm for complex numbered neural networks
[26] Trabelsi (2017) Deep complex networks
[29] Wisdom Powers (2016) Full-capacity unitary recurrent neural networks

### 2019-11-14 fragments/yang-ma-li.tex
typo fixes and references

>>>>

[03] Hirose (2003) Cmoplex valued neural networks: theories and applications
[04] Amin, Murase (2009) single layered complex-valued neural networks for real-valued classification problems
[05] Arjovsky, Shah (2016) Unitary evolution recurrent neural networks
[06] Danihelka, Wayne (2016) Associative Long short-term memory
[07] Wolter, Yao (2018) Complex gatteed recurrent nural network
[08] Wolter, Yao (2018) Fourier RNNs for sequence prediction
[09] Hochreiter, Schmidhuber (1997) Long short-term memory
[10] Cho, Merrienboer (2014) Learning phase representations using RNN encode-decoder for statistical machine translation
[11] Bahndau, Cho (2014) Neural Machine translation by jointly learning to align and translate
[12] Vaswani, Shazeer (2017) Attention is all you need
[13] Yang, Dai (2019) Xlnet: generalized autoregressive pretraining for language understsding
[18] Trabelsi (2017) Deep complex networks
